The following images are maps showing potential harmful algal blooms in {{value.to.match}} from `r date1` to `r date2`.

```{r include = FALSE}
# Filter by waterbody

# value.to.match <- '{{value.to.match}}' 

# Import processed remote sensing data and chl-a data
gee <- readRDS(paste0(drive_dir, "sensors_all_aggregated_", date1, "_", date2, ".RDS"))
# Add chl-a data as needed

gee <- gee %>% 
  filter(waterbody %in% value.to.match) %>%
  select(waterbody, everything())


#list of maps for each waterbody (some are split into two maps N and S)
nir_paths <- Sys.glob(paste0(drive_dir, "/nir_red/d_", date1, "_", date2, "/*.jpg"))
nir_paths <- nir_paths[grepl(value.to.match, nir_paths)]
nir_paths

fai_paths <- Sys.glob(paste0(drive_dir, "/fai_ndwi/*.jpg"))
fai_paths <- fai_paths[grepl(value.to.match, fai_paths)]

```


```{r echo = FALSE, out.width = '100%'}

knitr::include_graphics(nir_paths)

```
*NIR:Red mapped from `r date1` to `r date2` study period. Darker colors indicate higher NIR:Red exceedances. MON in the site name means monitor.*
  
  
```{r echo = FALSE, out.width = '100%'}
knitr::include_graphics(fai_paths)
```
*FAI-NDWI mapped from `r date1` to `r date2` study period. Darker colors indicate higher FAI-NDWI exceedances. MON in the site name means monitor.*
  
  
  At {{value.to.match}} timeseries data is processed for 4 locations as shown in Figure 3 below. At each monitoring point, 3 different timeseries are collected at 3 sites spaced 10m apart. These additional points are intended to minimize false positive threshold exceedances since vegetation at the water’s edge can confuse both algorithms.


```{r echo = FALSE, results = 'asis', out.width= '100%'}

ggplot(gee, 
       aes(date, nir_red_br, lty = pt_loc)) +
  geom_line() +
  geom_hline(yintercept = 1, color = "blue", lty = "dashed") +
  scale_linetype_discrete(name = "Point Location", 
                          labels = c("Edge", "Near edge", "Open water")) +
  theme_cowplot(12) +
  labs(x = "Date",
       y = "NIR:Red Ratio") +
  facet_wrap(~sampling_p, scales = "free_y")
```

NIR:Red time series from `r date1` to `r date2` study period. The blue dashed line is at NIR:Red = 1."

```{r include = FALSE}
# Count above thresholds
gee <- gee %>% 
  mutate(cyano = case_when(fai >= fai_thresh & ndwi >= ndwi_thresh ~ 1,
                           TRUE ~ 0))

over_thresh <- gee %>% 
  group_by(sampling_p, pt_loc) %>% 
  summarise(nir_red_n_over = sum(nir_red_br >= nir_red_thresh),
            fai_ndwi_n_over = sum(cyano),
            n_obs = n()) %>% 
  ungroup() %>%
  mutate(nir_red_pct_over = round(nir_red_n_over / n_obs * 100,1),
         fai_ndwi_pct_over = round(fai_ndwi_n_over / n_obs * 100,1)) %>%
  select(sampling_p, pt_loc, n_obs, nir_red_n_over, nir_red_pct_over, fai_ndwi_n_over, fai_ndwi_pct_over) %>%
  mutate(nir_combine = paste0(nir_red_n_over, " (", nir_red_pct_over, "%)"), 
         fai_combine = paste0(fai_ndwi_n_over, " (", fai_ndwi_pct_over, "%)"),
         n_obs = as.character(n_obs)) %>%
  select(sampling_p, pt_loc, n_obs, nir_combine, fai_combine) %>%
  rename("Point location" = "sampling_p",
         "Type" = "pt_loc",
         "Number of observations" = "n_obs",
         "NIR:Red exceedance count (%)" = "nir_combine",
         "FAI-NDWI exceedance count (%)" = "fai_combine")
  
```

```{r echo = FALSE, results = 'asis', tab.cap = "Mapped exceedances for each point location. NIR:Red values greater than 1 indicate an exceedance and FAI-NDWI output values greater than 0.63 indicate an exceedance."}


# Function to make table fit to page margins
fitflextabletopage <- function(ft, pgwidth = 6){
  ft_out <- ft %>% autofit()
  ft_out <- width(ft_out, width = dim(ft_out)$widths*pgwidth /(flextable_dim(ft_out)$widths))
  return(ft_out)
}

over_thresh %>%
  flextable() %>%
  fitflextabletopage

```

